Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-25 paper.qmd
Added tSNE proj for Gau

gen_axes <- function(data, proj_data, limits = 1) {

@@

@@

tr_from_to_df_gau1 <- tr_from_to_df_gau1 |>
  filter(row_number() != 115) |>
  filter(row_number() != 139)

@@

@@

projection <- cbind(
  c(-0.00215,-0.68905,-0.04778,-0.54223),
  c(0.42558,-0.23854,-0.63659,0.35753))

@@

axes_obj <- gen_axes(
  data = scaled_gau_data, 
  proj_data = projected_df, 
  limits = 1)

@@

five_gau_proj_tsne_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.18, 0.1)) +
  ylim(c(-0.78, -0.55)) +
  interior_annotation("a", 
                      position = c(0.08, 0.9),
                      cex = 3)

>>>>

gen_axes <- function(data, proj_data, limits = 1, axis_pos_x = NULL, axis_pos_y = NULL) {

@@

  axis_scale <- limits/6

  if (is.null(axis_pos_x)) {

    axis_pos_x <- -2/3 * limits

  if (is.null(axis_pos_y)) {

    axis_pos_y <- -2/3 * limits

@@

tr_from_to_df_gau1 <- tr_from_to_df_gau1 |>
  filter(row_number() != 149)

@@

benchmark_gau1 <- 0.1

@@

distance_df_small_edges <- distance_df_small_edges |>
  filter(row_number() != 108)

## First projection
projection <- cbind(
    c(0.46477,-0.02024,0.56378,0.39736),
    c(0.15607,-0.54876,-0.44090,0.41505))

@@

axes_obj <- gen_axes(
  data = scaled_gau_data, 
  proj_data = projected_df, 
  limits = 0.3,
  axis_pos_x = -0.4,
  axis_pos_y = -0.1)

@@

five_gau_proj_tsne_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.45, -0.2)) +
  ylim(c(-0.15, 0.18)) +
  interior_annotation("a", 
                      position = c(0.08, 0.9),
                      cex = 3)

## Second projection
projection <- cbind(
    c(-0.71895,0.29250,-0.29905,-0.01656),
    c(-0.16698,-0.62707,-0.23756,0.46328))

axes_obj <- gen_axes(
  data = scaled_gau_data, 
  proj_data = projected_df, 
  limits = 0.3,
  axis_pos_x = 0.1,
  axis_pos_y = -0.1)

five_gau_proj_tsne_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    alpha = 0.3) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(0.05, 0.25)) +
  ylim(c(-0.15, 0.25)) +
  interior_annotation("b", 
                      position = c(0.08, 0.9),
                      cex = 3)
